Maragra-CISM status report

### 2017-08-22 analyses/analyze_monthly_data.Rmd
update to raw data files

# Read data
clinic_agg <- maragra::clinic_agg

# Create date column
clinic_agg$date <- as.Date(paste0(clinic_agg$year, '-', clinic_agg$month, '-', 15))

# Create a percent postiive column
clinic_agg$percent_positive <- clinic_agg$positive / clinic_agg$tested * 100

# Arrange by date
clinic_agg <- clinic_agg %>% arrange(date)

# Get rid of any unknowns
clinic_agg <- clinic_agg %>% filter(!is.na(tested))
```

>>>>

# Read data
clinic_agg <- maragra::clinic_agg
```
